### 2014-10-03 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
San Francisco: Edits to flow path figure
San Francisco: Minor edit to flow path caption and acknowledgments

\begin{figure}[!ht]
\includegraphics[width=6.5in]{../Figures/Flow_Path_Top_Vel_462_s_First_Floor}
\includegraphics[width=6.5in]{../Figures/Flow_Path_Top_Vel_462_s_Basement_Floor}
\caption[Top view of the simulated flow path in the interior stairwell.]
{Top view of the simulated flow path on the first floor and basement floor 120~s after the first rear basement window failure. The arrows indicate the direction of flow. Two arrows located at a door or window indicate bi-directional flow at a vent opening. The maximum velocity is indicated by the red contour and corresponds to 9~m/s (20~mph).}
\label{fig:flow_path_top}
\end{figure}

@@

The authors would like to thank XXXX. The authors would also like to thank John Culbertson of Central Valley Fire District, MT, for his assistance in compiling Table~\ref{tab:LODD}. Finally, the authors would also like to thank Keith Stakes of NIST and Joseph Willi of the University of Illinois Urbana-Champaign for their assistance in creating the drawings of the structure.

>>>>

\begin{figure}[!ht]
\includegraphics[width=6.5in]{../Figures/Flow_Path_Top_Vel_462_s_First_Floor}
\includegraphics[width=6.5in]{../Figures/Flow_Path_Top_Vel_462_s_Basement_Floor}
\caption[Top view of the simulated flow path in the interior stairwell.]
{Top view of the simulated flow path on the first floor and basement floor 120~s after the first rear basement window failure. The arrows indicate the direction of flow. Two arrows located at a door or window indicate bi-directional flow at a vent opening. The dashed arrow indicates a continuation of flow from the basement towards the first floor. The velocity contours use the same scale as Figs.~\ref{fig:smv_velocity} and \ref{fig:smv_velocity_vectors} with a range of 0~m/s to 9~m/s (0~mph to 20~mph).}
\label{fig:flow_path_top}
\end{figure}

@@

The authors would like to thank XXXX. The authors would also like to thank John Culbertson of Central Valley Fire District, MT, for his assistance in compiling Table~\ref{tab:LODD}. Finally, the authors would like to thank Joseph Willi of the University of Illinois Urbana-Champaign for his assistance in creating the drawings of the structure.
